Systematic Design of Optimal Low-Thrust Transfers for the Three-Body Problem \thanks{This research has been supported in part by NSF under the grants CMMI-1243000 (transferred from 1029551), CMMI-1335008, and CNS-1337722.}

### 2017-01-18 manuscript.tex
Add more detail to the solution of the first example transfer
Issue #4

From the initial state on the periodic orbit, a series of optimal trajectories are generated to determine the reachable set.
By varying the angle \( \theta_d\) in~\cref{eq:constraints}, a different direction along the \Poincare section is maximized. 
We discretely vary the angle over the range \( \ang{0} \leq \theta_d < \ang{360} \) to approximate the reachability set of the spacecraft.
The intersection of the optimal trajectories as well as those of the target Moon orbit with the \Poincare section are shown in~\cref{fig:invariant_manifold_transfer}.

>>>>

From the initial state on the periodic orbit, a series of optimal trajectories are generated to determine the reachable set.
The multiple shooting approach is implemented to sovle the optimal control problem. 
We divide the time horizon into two equal length segments. 
The state trajectory is intialized using the free trajectory of the periodic orbit. 
Similarly, the costate trajectory is initialized from an initial guess of \( \vecbf{\lambda}_0 = \begin{bmatrix} -1 & -1 & -1 & -1\end{bmatrix}^T\) and propogated using the discrete equations of motion in~\cref{eq:costate_update}.
This results in the initial guess of the design vector \( \vecbf{\chi} = \begin{bmatrix} \vecbf{\lambda}_0 & \vecbf{x}_1^{-} & \vecbf{\lambda}_1^{-} & \vecbf{\beta} \end{bmatrix}^T\).
This design vector is then varied to ensure that the necessary conditions of optimality and the interior point constraints are satisfied.

By varying the angle \( \theta_d\) in~\cref{eq:constraints}, a different direction along the \Poincare section is maximized. 
We discretely vary the angle over the range \( \ang{0} \leq \theta_d < \ang{360} \) to approximate the reachability set of the spacecraft.
Choosing a new angle \( \theta_d \) corresponds to a different direction as well as a new optimal control problem which is again solved using the multiple shooting approach laid out previously.
The intersection of the optimal trajectories as well as those of the target Moon orbit with the \Poincare section are shown in~\cref{fig:invariant_manifold_transfer}.
